---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(flair)
library(magrittr)
knitr::opts_chunk$set(include = TRUE)
```

## Lists

Lists are a another type of data structure. It can store other objects like `characters`, `logical`, `numeric`.

Each of the items in the list has a spot in the list. This is called an "index". An index is a number from 1 to the length of the list. 

Note - Different programming languages count this differently. For R it starts counting at 1.

For a list called `ocean`. the character `whale` has an index of 2.

```{r list}
ocean <- c("otter", "whale", "jellyfish")
#index        1          2         3
```

If you want an item in the list you can ask R for it using the index.

```{r index, echo=FALSE}
decorate('
ocean[2]
') %>%
  flair("2")
```

### other useful ways of interacting with lists
#### `length()`
Get the `length` of the list
```{r}
length(ocean)
```

#### **Splicing lists** `:`

You can get part of a list by specifying the indexes you want.
```{r}
ocean[2:3]
```

Once trick to avoid hard coding values is to use `length` to get the last index in the list.
```{r, echo=FALSE}
decorate('
ocean[2:length(ocean)]
') %>%
  flair("length(ocean)")
```

#### `which()`
figuring out the index if you know the character
```{r}
which(ocean == "otter")
```

### Exercise 
There is some list called `flavours`. Please answer the following questions about this list:

1. How many items are in `flavours`
2. What is the index of `yuzu`
3. What is in the index 4?
```{r, include=FALSE}
flavours <- c("matcha", "sesame", "yuzu", "chocolate", "cherry")
```

```{r flavours, exercise=TRUE, exercise.eval=FALSE}
flavours
```

```{r flavours-hint}
#1
length(flavours)
#2
which(flavours == "yuzu")
#3
flavours[4]
```

## `for` Loops

```{r structure, echo=T, eval=F}
for (variable in vector) {
  #do something here
}
```

What actually happens behind the scenes:
```{r loop-ex, echo=FALSE, collapse=TRUE}
decorate('c("otter", "whale", "jellyfish")') %>% 
  flair(ocean[1])

decorate('c("otter", "whale", "jellyfish")') %>% 
  flair(ocean[2])

decorate('c("otter", "whale", "jellyfish")
                  #    1         2        3') %>% 
  flair(ocean[3])
```

Two ways to work through lists
```{r print example, echo=T}
ocean <- c("otter", "whale", "jellyfish")

for (animal in ocean) {
  print(animal)
}

for (animal in 1:length(ocean)) {
  print(animal)
}
```

```{r}
for (animal in ocean) {
  print(paste(animal, "in the ocean"))
}

for (i in 1:length(ocean)) {
  print(paste(ocean[i], "in the ocean"))
}
```


### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## `apply and map`

## `if else`
